---
title: "CHOL"
author: "Angela Andaleon"
output: html_document
---
##EDIT QCSTEP2 LINE
##In RStudio

```{r CHOL}
data <- read.table("/home/angela/GWAS/Phenotypes/YRI_phenotypes.txt", header = T)
hist(data$CHOL)
	##Found in /home/angela/GWAS/CHOL/hist_CHOL.pdf
shapiro.test(data$CHOL)
	##W = 0.99298, p-value = 9.258e-05"
	##Note: using log2 and log10 produces "p-value = 8.722e-09"
```

##In command line

```{bash pheno}
plink --bfile /home/angela/QC/QCStep2/QCStep2 --maf 0.05 --linear --adjust --pheno /home/angela/GWAS/Phenotypes/YRI_phenotypes.txt --pheno-name CHOL --out /home/angela/GWAS/CHOL/CHOL
```

##In RStudio

```{r CHOL}
CHOL_linear <- read.table("/home/angela/GWAS/CHOL/CHOL.assoc.linear", header = T)
CHOL_linear_noNA <- CHOL_linear[complete.cases(CHOL_linear),]
dev.off()
source("/home/angela/GWAS/qqman.r")
png(filename="/home/angela/GWAS/CHOL/CHOL_qq.png", res=100)
qq(CHOL_linear_noNA$P)
	##In "/home/angela/GWAS/CHOL/CHOL_qq.png"
dev.off()
source("/home/angela/GWAS/qqman.r")
manhattan(CHOL_linear_noNA)
	##In "/home/angela/GWAS/CHOL/CHOL_man.png"
dev.off()