---
title: "TRIG"
author: "Angela Andaleon"
output: html_document
---
##EDIT QCSTEP2 LINE
##EDIT TO INCLUDE LOG ANALYSES
##In RStudio

```{r TRIG}
data <- read.table("/home/angela/GWAS/Phenotypes/YRI_phenotypes.txt", header = T)
hist(data$TRIG)
	##Saved to "/home/angela/GWAS/TRIG/hist_TRIG.pdf"
shapiro.test(data$TRIG)
	##"W = 0.82521, p-value < 2.2e-16" (!)
	##For log10, "W = 0.97811, p-value = 2.727e-11"
```

##In command line

```{bash pheno}
plink --bfile /home/angela/QC/QCStep2/QCStep2 --maf 0.05 --linear --adjust --pheno /home/angela/GWAS/Phenotypes/YRI_phenotypes.txt --pheno-name TRIG --out /home/angela/GWAS/TRIG/TRIG
```

##In RStudio

``` {r TRIG}
TRIG_linear <- read.table("/home/angela/GWAS/TRIG/TRIG.assoc.linear", header = T)
TRIG_linear_noNA <- TRIG_linear[complete.cases(TRIG_linear),]
source("/home/angela/GWAS/qqman.r")
qq(TRIG_linear_noNA$P)
	##Saved to "/home/angela/GWAS/TRIG/TRIG_qq.png"
dev.off()
source("/home/angela/GWAS/qqman.r")
manhattan(TRIG_linear_noNA)
	##Saved to "/home/angela/GWAS/TRIG/TRIG_man.png"
